Halving the cost of quantum addition

### 2018-01-19 paper.tex
Polish the abstract

\begin{abstract}
We improve the number of T gates needed to perform an $n$-bit adder from $8n + O(1)$ \citep{Amy2013, Cuccaro2004, AustinDiscussionsAndEmails2017} to $4n + O(1)$.
We do so via a ``temporary logical-AND" construction (a reframing of a result by Jones \cite{Jones2013}) which uses four T gates to store the logical-AND of two qubits into an ancilla and zero T gates to later erase the ancilla.
Temporary logical-ANDs are a generally useful tool when optimizing T-counts.
They can be applied to integer arithmetic, modular arithmetic, rotation synthesis, the quantum Fourier transform, Shor's algorithm, Grover oracles, and many other circuits.
Because T gates dominate the cost of quantum computation based on the surface code, and temporary logical-ANDs are widely applicable, our constructions represent a significant reduction in projected costs of quantum computation.
We also present an $n$-bit controlled adder circuit with T-count of $8n + O(1)$, a temporary adder that can be computed for the same cost as the normal adder but whose result can be kept until it is later uncomputed without using T gates, and discuss some other constructions whose T-count is improved by the temporary logical-AND.
\end{abstract}

>>>>

\begin{abstract}
We improve the number of T gates needed to perform an $n$-bit adder from $8n + O(1)$ \citep{Amy2013, Cuccaro2004, AustinDiscussionsAndEmails2017} to $4n + O(1)$.
We do so via a ``temporary logical-AND" construction which uses four T gates to store the logical-AND of two qubits into an ancilla and zero T gates to later erase the ancilla.
This construction is equivalent to one by Jones \cite{Jones2013}, except that our framing makes it clear that the technique is far more widely applicable than previously realized.
Temporary logical-ANDs can be applied to integer arithmetic, modular arithmetic, rotation synthesis, the quantum Fourier transform, Shor's algorithm, Grover oracles, and many other circuits.
Because T gates dominate the cost of quantum computation based on the surface code, and temporary logical-ANDs are widely applicable, this represents a significant reduction in projected costs of quantum computation.
In addition to our $n$-bit adder, we present an $n$-bit controlled adder circuit with T-count of $8n + O(1)$, a temporary adder that can be computed for the same cost as the normal adder but whose result can be kept until it is later uncomputed without using T gates, and discuss some other constructions whose T-count is improved by the temporary logical-AND.
\end{abstract}
